---
title: "ALA Workshop"
subtitle: ""
author: "Stockholm, Swedish Museum of Natural History"
date: "May 2017"
output:
  tint::tintHtml: 
     self_contained: TRUE
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tint)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))

options(htmltools.dir.version = FALSE)

fig <- function(fig_path) {

	library(ggplot2)
	r <- as.raster(readbitmap::read.bitmap(fig_path))

	ggplot() +
		annotation_raster(r, -Inf, Inf, -Inf, Inf, interpolate = TRUE) +
		theme(plot.background = element_blank()) +
		theme_void()
}

```


```{r fig-nocap-fullwidth-1, echo = FALSE, fig.fullwidth=TRUE, fig.width=12, cache=FALSE}
fig("fig/stockholm.jpg")
```

In May 2017, a technical workshop about customization of biodiversity portals based on the Atlas of Living Australia code is planned to be held in Stockholm. 

This workshop is co-arranged with the 9th European GBIF Node meeting ^[see [European GBIF Node meeting](https://bioatlas.se/registration-is-open-to-the-9th-european-gbif-nodes-meeting/) announcement].


```{r fig-nocap-margin-before-first, fig.margin=TRUE, fig.width=2, fig.height=2, cache=FALSE, echo=FALSE}
fig("fig/gbif-logo.jpg")
```

# Suggested Topics

`r newthought('The workshop ')` is planned to cover some topics related to DevOps of biodiversity portals based on [Atlas of Living Australia code](https://github.com/AtlasofLivingAustralia). 

Currently proposed topics for the workshop sessions include subjects related to customizing a national portal based on the Atlas of Living Australia software using tools such as Docker for automating builds and releases. 

We also plan to discuss how to integrate external services and approaches for customizing existing Atlas components with language translations and other national customizations.

# Participation

`r newthought('Participants are invited')` to collaborate in shaping the agenda. 

You can register your participation using [the registration page](http://www.nrm.se/english/researchandcollections/bioinformaticsandgenetics/europeangbifnodesmeeting.9004194.html).


# Agenda

[Current Agenda](agenda)

# Contact details

Feel free to get in touch to discuss the event using these contact details:

Anders Telenius  
Node manager  
__anders.telenius(at)nrm.se__

Veronika Johansson  
Project assistant/Data manager  
__veronika.johansson(at)nrm.se__

Manash Shah  
Software developer  
__manash.shah(at)nrm.se__
