---
title: "ALA Workshop"
subtitle: ""
author: "Stockholm, Swedish Museum of Natural History"
date: "May 2017"
output:
  tint::tintHtml: 
     self_contained: TRUE
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tint)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))

options(htmltools.dir.version = FALSE)

fig <- function(fig_path) {

	library(ggplot2)
	r <- as.raster(readbitmap::read.bitmap(fig_path))

	ggplot() +
		annotation_raster(r, -Inf, Inf, -Inf, Inf, interpolate = TRUE) +
		theme(plot.background = element_blank()) +
		theme_void()
}

```


```{r fig-nocap-fullwidth-1, echo = FALSE, fig.fullwidth=TRUE, fig.width=12, cache=FALSE}
fig("fig/stockholm.jpg")
```

In May 2017, a workshop about customization of biodiversity portals based on the Atlas of Living Australia code is planned to be held in Stockholm. This workshop is co-arranged with the 9th European GBIF Node meeting ^[see [European GBIF Node meeting](https://bioatlas.se/registration-is-open-to-the-9th-european-gbif-nodes-meeting/) announcement].


```{r fig-nocap-margin-before-first, fig.margin=TRUE, fig.width=2, fig.height=2, cache=FALSE, echo=FALSE}
fig("fig/gbif-logo.jpg")
```

# Suggested Topics

`r newthought('The workshop ')` is planned to cover some topics related to DevOps of biodiversity portals based on [Atlas of Living Australia code](https://github.com/AtlasofLivingAustralia). Currently proposed topics include subjects related to using Docker, to automate builds and releases and also how to integrate external services and how to customize existing Atlas components with language translations and other national customizations:

- Docker Fundamentals

- Building and Releasing using Continuous Integration processes (using make, git, travis and docker)

- Adding "non-core" components to the system composition 

- Upgrading indvidual ALA components to new releases

- Customizing ALA components and packaging using Docker - experiences from BioAtlas.se in Sweden.

- Experiences from internationalization (I18N) and national customizations of ALA modules

- Building a nationally customized taxonomic backbone based on the Atlas name indexing module

- Tools for testing performance and scanning system components

- Spatial Portal - recommended practices for setting up layers etc

- Integrating Mirroreum - a web-based biodiversity analysis platform for reproducible research

- Discussions - Overiew of Work in progress and Future Works

# Participation

`r newthought('Participants are invited')` to collaborate in shaping the agenda. 

You can register your participation using [the registration page](http://www.nrm.se/english/researchandcollections/bioinformaticsandgenetics/europeangbifnodesmeeting.9004194.html).

# Contact details

Feel free to get in touch to discuss the event using these contact details:

Anders Telenius  
Node manager  
__anders.telenius(at)nrm.se__

Veronika Johansson  
Project assistant/Data manager  
__veronika.johansson(at)nrm.se__

Manash Shah  
Software developer  
__manash.shah(at)nrm.se__
